%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

	%---------------------------------------------------------
	\cventry
	{Graduate Research Assistant} % Job title
	{ICS--FORTH} % Organization
	{Heraklion, Greece} % Location
	{Sep. 2017 - Present} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Evaluate approaches to expanding memory address space for
			            JVM-based large-scale data analytics frameworks using fast storage
			            devices.}
			\item{Implement an extra storage level on Apache Spark
			            to cache data off-heap on non-volatile memories.}
			\item{Design and implement of TeraHeap, a system that extends the JVM to
			            use a a second high-capacity managed heap over an NVMe SSD alongside
			            the regular heap in DRAM to reduce memory pressure in big data
			            frameworks.}
			\item{Designed and implemented FlexHeap, an I/O-aware heap resizing
			            mechanism for G1 that dynamically partitions DRAM between the JVM heap
			            and the OS page cache.}
			\item{Designed and implemented SmartSweep, a JVM garbage collection
			            mechanism that reclaims space in tiered managed heaps using approximate
			            region-level liveness, avoiding remote heap scans.}
			\item{\textbf{Supervision:} Angelos Bilas and Polyvios Pratikakis}
		\end{cvitems}
	}

	%---------------------------------------------------------
	\cventry
	{Undergraduate Research Assistant} % Job title
	{ICS--FORTH} % Organization
	{Heraklion, Greece} % Location
	{Jan. 2017 - Aug. 2017} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Schedule techniques for data placement for large scale
			            graph analytics (Apache Spark GraphX).}
			\item{\textbf{Supervisor:} Polyvios Pratikakis}
		\end{cvitems}
	}
	%---------------------------------------------------------

	%---------------------------------------------------------
\end{cventries}
