
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}

\cvsubsection{Full Papers / Articles \dotfill}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cventries}
	% %---------------------------------------------------------
	% \cventry
	% {}
	% {}
	% {}
	% {}
	% {\textbf{Iacovos G. Kolokasis}, Shoaib Akram, Foivos Zakkak, Polyvios
	% 	Pratikakis, and Angelos Bilas. When Garbage Collection Isn’t the Only
	% 	Bottleneck: Managed Heap Resizing with I/O Awareness. (Under submission to
	% 	PLDI '26).}
	% {}
	%---------------------------------------------------------
	\cventry
	{}
	{}
	{}
	{}
	{Alexandros Emmanouil Antonakakis, \textbf{Iacovos G. Kolokasis}, Foivos S. Zakkak,
		Angelos Bilas, Polyvios Pratikakis  2025.  MaTSa: Race Detection in Java.
		Proceedings of the 17th ACM SIGPLAN International Workshop on Virtual
		Machines and Intermediate Languages (VMIL ‘25), October 12--18, 2025,
		Singapore, Singapore.}
	{}
	%---------------------------------------------------------
	\cventry
	{}
	{}
	{}
	{}
	{\textbf{Iacovos G. Kolokasis}, Konstantinos Delis, Shoaib Akram, Foivos S.
		Zakkak, Polyvios Pratikakis, and Angelos Bilas. 2025. SmartSweep: Efficient
		Space Reclamation in Tiered Managed Heaps. In Proceedings of the 22nd ACM
		SIGPLAN International Conference on Managed Programming Languages and
		Runtimes (MPLR '25), October 12--18, 2025, Singapore, Singapore.}
	{}
	%---------------------------------------------------------
	\cventry
	{}
	{}
	{}
	{}
	{\textbf{Iacovos G. Kolokasis}, Giannos Evdorou, Shoaib Akram,
		Christos Kozanitis, Anastasios Papagiannis, Foivos Zakkak,
		Polyvios Pratikakis, and Angelos Bilas. TeraHeap: Exploiting Flash Storage for
		Mitigating DRAM Pressure in Managed Big Data Frameworks. ACM Transactions on
		Programming Languages and Systems (TOPLAS).}
	{}
	\cventry
	{}
	{}
	{}
	{}
	{\textbf{Iacovos G. Kolokasis}, Giannos Evdorou, Shoaib Akram,
		Christos Kozanitis, Anastasios Papagiannis, Foivos Zakkak,
		Polyvios Pratikakis, and Angelos Bilas. TeraHeap: Reducing Memory
		Presure in Managed Big Data Frameworks. In Proceedings of the 28th
		ACM International Conference on Architectural Support for
		Programming Languages and Operating Systems, Volume 3 (ASPLOS ’23),
		March 25--29, 2023, Vancouver, BC, Canada.}
	{}
	\cventry
	{}
	{}
	{}
	{}
	{\textbf{Iacovos G. Kolokasis}, Anastasios Papagiannis, Foivos
		Zakkak, Polyvios Pratikakis, and Angelos Bilas.%
		Say Goodbye to Off-heap Caches! On-heap Caches Using Memory-Mapped
		I/O. In Presented as part of the 12th USENIX Workshop on Hot
		Topics in Storage and File Systems (HotStorage '20), Boston, MA,
		2020. USENIX. (\textbf{Best Presentation Award})}
	{}
	\cventry
	{}
	{}
	{}
	{}
	{\textbf{Iacovos G. Kolokasis} and Polyvios
		Pratikakis. Cut to Fit: Tailoring the Partitioning to the
		Computation. 2nd Joint International Workshop on Graph Data
		Management Experiences \& Systems (GRADES) and Network Data
		Analytics (NDA), June 30-July 2019, Amsterdam, Netherlands}
	{}

	%---------------------------------------------------------
\end{cventries}

%---------------------------------------------------------
\cvsubsection{Posters \dotfill}

\vspace{-15pt}
\begin{cventries}
	%---------------------------------------------------------
	\cventry
	{}
	{}
	{}
	{}
	{\textbf{Iacovos G. Kolokasis}, Shoaib Akram, Foivos
		Zakkak, Polyvios Pratikakis, and Angelos Bilas.% 
		DynaHeap: Dynamic Division of DRAM between Heterogeneous Managed Heaps.
		19th European Conference on Computer Systems (EuroSys '24).
	}
	{}

	\cventry
	{}
	{}
	{}
	{}
	{\textbf{Iacovos G. Kolokasis}, Shoaib Akram, Foivos
		Zakkak, Polyvios Pratikakis, and Angelos Bilas.% 
		DynaHeap: Dynamic Division of DRAM between Heterogeneous Managed Heaps.
		29th ACM Symposium on Operating Systems Principles (SOSP '23).
	}
	{}

	\cventry
	{}
	{}
	{}
	{}
	{\textbf{Iacovos G. Kolokasis}, Anastasios Papagiannis, Foivos
		Zakkak, Shoaib Akram, Christos Kozanitis, Polyvios Pratikakis, and Angelos Bilas.% 
		TeraCache: Efficient Caching over Fast Storage Devices.
		MSR Cambridge PhD Virtual Workshop on Next-Generation Cloud Infrastructure'21.
	}
	{}

	\cventry
	{}
	{}
	{}
	{}
	{\textbf{Iacovos G. Kolokasis}, Anastasios Papagiannis, Foivos
		Zakkak, Polyvios Pratikakis, and Angelos Bilas.% 
		Garbage
		Collection or Serialization? Between a Rock and a Hard Place!
		16th International Summer School on Advanced Computer Architecture
		and Compilation for High-Performance and Embedded Systems
		(ACACES).}
	{}

	%---------------------------------------------------------
\end{cventries}

%---------------------------------------------------------
\cvsubsection{Technical Reports \dotfill}

\vspace{-15pt}
\begin{cventries}
	%---------------------------------------------------------

	\cventry
	{}
	{}
	{}
	{}
	{\textbf{Iacovos G. Kolokasis} and Polyvios Pratikakis.
		Cut to Fit: Tailoring the Partitioning to the Computation.
		Technical Report 469, ICS -- FORTH, Apr 2018 }{}%


	%---------------------------------------------------------
\end{cventries}
